### 2017-05-16 Doc/classicthesis/Chapters/Draft.tex
last interactions
results finish

% TODO : table y gráfico

@@

% TODO: gráfico y tabla

\begin{figure}[bth]
	\myfloatalign
	\subfloat[Times and relative speedup]
	{\includegraphics[width=.45\linewidth]{gfx/graphics/createSCtable}} \quad
	\subfloat[Comparison graph]
	{\includegraphics[width=.4\linewidth]{gfx/graphics/createSC}} \\
	\caption{Create smart card times (seconds)}
	\label{fig:createSmartCard:graph}
\end{figure}

The RPi3 is about 16 times slower than the laptop in the creation of the \textit{SoftwareSmartcard}, but almost 9 times faster than the setup of the smart card in the Omega2 using APDUs. This gives us that the laptop is 145 times faster than the combination of RPi3 and Omega2.

@@

This is the first interaction between the RPi3 and the Omega2 IoT smart card, using 30 APDU Commands, and Responses, as shown in \autoref{fig:APDUsInitIoTSC}, with a total of 1109 bytes exchanged. From our network benchmark, using TCP sockets, the delay in the transmission is only around 15 and 20 ms, negligible as we said compared to the almost 20 seconds the operation lasts.

\paragraph{Issuing of the credential}
%TODO
\begin{figure}[bth]
	\begin{center}
		\includegraphics[width=\linewidth]{gfx/IssuanceInteraction}
	\end{center}
	\caption{Issuance interaction.}
	\label{fig:IssuanceInteraction}
\end{figure}

@@

\paragraph{Presentation}
%TODO

@@

>>>>

\begin{figure}[bth]
	\myfloatalign
	\subfloat[Times and relative speedup]
	{\includegraphics[width=\linewidth]{gfx/graphics/setuptable}} \quad
	\subfloat[Comparison graph]
	{\includegraphics[width=.8\linewidth]{gfx/graphics/setup}} \\
	\caption{Setup times (milliseconds)}
	\label{fig:setup:graph}
\end{figure}

@@

\begin{figure}[bth]
	\myfloatalign
	\subfloat[Times and relative speedup]
	{\includegraphics[width=0.5\linewidth]{gfx/graphics/createSCtable}} \quad
	\subfloat[Comparison graph]
	{\includegraphics[width=0.45\linewidth]{gfx/graphics/createSC}} \\
	\caption{Create smart card times (seconds)}
	\label{fig:createSmartCard:graph}
\end{figure}

From \autoref{fig:createSmartCard:graph} we see that the RPi3 is about 16 times slower than the laptop in the creation of the \textit{SoftwareSmartcard}, but almost 9 times faster than the setup of the smart card in the Omega2 using APDUs. This gives us that the laptop is 145 times faster than the combination of RPi3 and Omega2 in our IoT deployment.
But looking at the times, this process lasts up to 20 seconds, making it something feasible.

@@

This is the first interaction between the RPi3 and the Omega2 IoT smart card, \textbf{using 30 APDU Commands, and Responses}, as shown in \autoref{fig:APDUsInitIoTSC}, with a total of $1109$ bytes exchanged. From our network benchmark, using TCP sockets, the delay in the transmission is only around 15 and 20 ms, negligible as we said compared to the almost 20 seconds the operation lasts.

\paragraph{Issuing of the credential}
The issuance is done in three steps for the User service, shown in \autoref{fig:IssuanceInteraction} with a red note showing the start of each step for the User delegation, in green for the interactions between Issuer and User, and the darker red is the Identity service, choosing the first available identity to use. The arrows in the figure show the REST calls performed during the test, where the IoT device acts as User, the RPi3 hosts the P2ABCE delegation services and the laptop is the Issuer.

The three delegation steps and the REST method called are:

\begin{center}
	\begin{tabular}{l|l}
	First issuance protocol step & $/issuanceProtocolStep$ \\
	Second issuance protocol step  & $/issuanceProtocolStepUi$ \\
	\textit{(end of first step for the User)} & \\
	Third issuance protocol step & $/issuanceProtocolStep$ \\
	\textit{(second step for the User)}  & \\
\end{tabular}
\end{center}

\begin{figure}[bth]
	\begin{center}
		\includegraphics[width=\linewidth]{gfx/IssuanceInteraction}
	\end{center}
	\caption{Issuance interaction.}
	\label{fig:IssuanceInteraction}
\end{figure}

@@

As we can see, the three REST calls to the delegation User service involve communication with the smart card. We show in \autoref{fig:IssuanceAPDUs} the APDU Commands for each REST call.
There are 45 APDU Commands in total, $3197$ bytes exchanged, that would introduce a latency of 45ms in the network, negligible.

\begin{figure}[bth]
	\myfloatalign
	\subfloat[Times (ms) and relative speedup]
	{\includegraphics[width=\linewidth]{gfx/graphics/issuancetable}} \quad
	\subfloat[Comparison graph]
	{\includegraphics[width=.8\linewidth]{gfx/graphics/issuance}} \\
	\caption{Issuance times (milliseconds)}
	\label{fig:issuance:graph}
\end{figure}

In \autoref{fig:issuance:graph} we have the times spent in each REST call. The laptop shows again to be many times faster than the other two scenarios, but the times are again feasible even for the IoT environment.

Lets compare the Raspberry Pi 3 and the Omega2 executions. There is a correlation between the number of APDU Commands needed in each step with the increment in time when using the IoT smart card, that is, how much the delegation server.

The first one only involved one APDU, with $33$ bytes total (Command and Response), and times are almost identical. The second call needed $34$ APDUs, with $1623$ bytes, and the increase in time is around tree times slower than the RPi3 on its own. The third call used $20$ APDUs, $1541$ bytes, and makes the IoT scenario almost 7 times slower.

The analysis shows where there are more cryptographic operations involving the Omega2, and because the amount of data exchanged is minimal, the difference in processing power between Omega2 and Raspberry Pi 3 is clear.

\paragraph{Presentation token}
The final step of the test involves a Prove, or Presentation in P2ABCE, where the Verifier sends the User or Prover the Presentation Policy, and the User answers with the Presentation Token, without more steps. In \autoref{fig:ProvingInteraction}, using the same colors as in the Issuance interaction, we can see the delegation messages done by the Omega2.

In \autoref{fig:APDUsProving} the APDU Commands for each step are shown, $28$ in total, $1939$ bytes, $27$ms approx. in the network.

\begin{figure}[bth]
	\begin{center}
		\includegraphics[width=\linewidth]{gfx/ProvingInteraction}
	\end{center}
	\caption{Proving interaction.}
	\label{fig:ProvingInteraction}
\end{figure}

@@

Again, as shown in \autoref{fig:proving:graph}, there is a correlation between the number of APDU Commands used, the work the IoT smart card must perform, and the time measured. The $20$ APDU Commands in the first call make the IoT deployment almost $8$ times slower than the Raspberry Pi 3; but with only $8$ APDU Commands, the second one is less than $1.5$ times slower.

Nonetheless, it's significant the difference in performance between the laptop and the Raspberry Pi 3 in the last REST call, more than $40$ times slower, even using the \textit{SoftwareSmartcard}.

\begin{figure}[bth]
	\myfloatalign
	\subfloat[Times (ms) and relative speedup]
	{\includegraphics[width=.8\linewidth]{gfx/graphics/provingtable}} \quad
	\subfloat[Comparison graph]
	{\includegraphics[width=.7\linewidth]{gfx/graphics/proving}} \\
	\caption{Proving times (milliseconds)}
	\label{fig:proving:graph}
\end{figure}

Unlike the previous steps, the Presentation or Proving is done more than once, being the key feature of ZKP protocols. The laptop performs a prove in less than one second, the RPi3 needs $15$ seconds, but our P2ABCE IoT deployment needs $15$ seconds for the first step, and $18$s for the second step, $33$ seconds total to generate a Presentation Token.

\paragraph{Memory usage on the Omega2}
Using the tool \textit{time -v} we can get a lot of useful information about a program, once it finishes. In our case, the binary with BIOSC and the smart card logic starts as an empty smart card, goes through the described process, and then we can stop it, as the User Service won't use it anymore.

After another round of tests, now using \textit{time -v}, the field named \textit{Maximum resident set size (kbytes)} shows the \textbf{maximum} size of RAM used by the process since its launch. In our case, this involves the use of static memory for the \textit{global variables} of the smart card logic, and the dynamic memory used by the third party libraries, like GMPlib, OpenSSL and cJSON.

GMP and OpenSSL always allocate the data in their own ADT, what involves copying the arrays of bytes representing the big modular integers from the cryptographic operations. cJSON, used in the serialization of the smart card for storage, and debug being human readable, stores a copy of every saved variable in the JSON tree structure, then creates a string (array of char) with the JSON, that the user can write to a file.

Understanding the many bad uses of memory done in this PoC is important for future improvements and ports. A custom modular library using the same array of bytes that the smart card logic, a binary serialization, and many improvements, are our future work.

With all that said, the mean of the maximum memory usage measured is $6569.6$ kbytes. Compared to the $64$MB of RAM available in the Omega2, our PoC could be executed in more constrained devices, given the system is compatible.

%%%%%%%%%%%%%%%%%%%%%%%

% Consideraciones futuras: implementar directamente Smartcard interface vs seguir usando APDUs:  minimizan uso de red, facilitan protocolo de comunicación de las APDUs, son estándar, mejoran el mantenimiento del código: P2ABCE puede cambiar las interfaces, pero mantendrá compatibilidad con las smartcards, si implementamos Smartcard.java por cada cambio en la interfaz deberemos actualizar cada IoT smart card.
